IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-03 review/response_2.tex

		\begin{response}
			For the single-user case, direct optimization on $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ is possible. The reviewer is referred to Algorithm 1 of \cite{M-Clerckx2018b} for more details, and the idea is briefly described as follows. First, $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ are complex variables of size $MN \times 1$. To enable GP tools (which apply to problems involving real-valued variables), we notice that the optimal phase of $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ should be designed to compensate the phase of the corresponding composite channel $\boldsymbol{h}$, namely
			\begin{equation}
				\arg(\boldsymbol{w}_{\mathrm{I}}) = \arg(\boldsymbol{w}_{\mathrm{P}}) = -\arg(\boldsymbol{h}),
			\end{equation}
			such that, from the perspective of phase design, the current expression \ref{M-eq:z_expand} is maximized (where all $\cos$ terms peak at \num{1}) and the rate expression is maximized (where the phases align with those of matched filters). Therefore, the direct optimization on $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ boils down to amplitude optimization on $\boldsymbol{s}_{\mathrm{I}}$ and $\boldsymbol{s}_{\mathrm{P}}$, where $\boldsymbol{s}_{\mathrm{I/P}}=\lvert \boldsymbol{w}_{\mathrm{I/P}} \rvert$. GP tools can be applied at this stage and the number of real-valued variables are $2MN$. In contrast, the proposed Algorithm~\ref{M-al:gp} decoupled the design in the spatial and frequency domains, derived the global optimal active precoder, and leaves an resource allocation issue with $2N$ real-valued variables in the frequency domain. Since the computational complexity of GP scales exponentially with the number of variables, optimizing $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ as a whole can be very inefficient and not discussed in the manuscript. Accordingly, we have revised the manuscript as follows.
			\begin{framed}
				To avoid straightforward optimization over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$, we decouple the waveform in the spatial and frequency domains to reduce the size of variables.
			\end{framed}
		\end{response}

@@

		\begin{point}
			In the low-complexity BCD, it is unclear how the authors dealt with the optimization of $\rho$ and $\delta$. In Algorithm~\ref{M-al:lc_bcd}, both of them are input. Did the authors perform a two-dimensional search here? Besides, they were assumed to be identical in the simulation. How will this assumption influence the performance loss?
		\end{point}

		\begin{response}
			Thank you for raising this point. The combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter, while the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver. We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point. Heuristically, $\delta$ and $\rho$ should approximately equal at each point to boost R-E tradeoff. Indeed, the LC-BCD algorithm intends to draw the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{0} to \num{1}. However, based on the deduction above, we set $\delta=\rho$ is the simulation and obtain the R-E region by one-dimensional search instead. The results show that even a one-dimensional search for the LC-BCD algorithm can achieve a very good performance. We have summarized the point in the manuscript as follows.
			\begin{framed}
				\textellipsis where the combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver\footnotemark.

				\textellipsis and the LC-BCD algorithm characterizes the R-E tradeoff via two-dimensional search over $\delta$, $\rho$ from \num{0} to \num{1}.

				\textellipsis assume $\delta=\rho$ for simplicity (thus one-dimensional search for the R-E region).

				\textellipsis  \emph{Third,} the LC-BCD algorithm achieves a decent R-E region even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}, which achieves a good balance between performance and complexity.
			\end{framed}
			\footnotetext{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point. Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}
		\end{response}

@@

		\begin{point}
			It was shown via simulation that PS is not always superior to TS, unlike the linear model. Is it possible to develop some analytical preconditions to determine which one is better?
		\end{point}

		\begin{response}
			We concluded that PS outperforms TS when the number of subcarrier is relatively small or when the SNR is relatively large. However, the analytical preconditions in the proposed system can be very hard to obtain because SNR can depend on many factors (e.g., distance of all paths, number of IRS elements, average noise power, etc.). Essentially, this behavior origins from the waveform selection and we would like to analyze it in a nutshell.

			TS only performs a naive time-sharing between the WIT point and the WPT point. At the WIT point, only modulated waveform is used to maximize the achievable rate. At the WPT point, the optimal waveform depends on the number of subcarriers $N$. Although the modulated waveform has an modulation gain of \num{2} that outstands for a small $N$, it creates no DC coupling between frequencies and is outperformed by multisine for a large $N$. Therefore, for a relatively small $N$, the modulated waveform is used at both WIT and WPT point, and one can heuristically infer that no multisine waveform is needed for any point (this is verified in simulation). In this case, the R-E region is convex, which aligns with the conventional linear harvester model (PS outperforms TS and dedicated power waveform is unnecessary). However, as $N$ becomes sufficiently large, multisine waveform further boosts the WPT point due to its power benefit under nonlinear harvester model. It creates some concavity in the high-power region and accounts for the superiority of TS.

			Similar effect exists for SNR. At high SNR, the SWIPT user can achieve a decent rate even if a small fraction of transmit power is allocated to the modulated waveform. Therefore, one can approach high-rate region fast at a small cost of DC power at high SNR. This is however impossible at low SNR.

			The manuscript has been updated as follows.
			\begin{framed}
				\emph{Second,} the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\ref{M-fi:re_subband}). When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can deduct that no multisine waveform is needed for the entire R-E region. It aligns with the conventional linear harvester model where the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary. As $N$ becomes sufficiently large, multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model. Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
			\end{framed}
		\end{response}

@@

		\begin{response}
			We agree with the reviewer that the signal model requires more description. The manuscript has been updated as follows.
			\begin{framed}
				As suggested in \cite{M-Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency. The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
				\begin{equation}
					\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
				\end{equation}
				where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$. On the other hand, the power signal transmitted over subband $n$ at time $t$ is
				\begin{equation}
					\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
				\end{equation}
				where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
				\begin{equation}
					\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
				\end{equation}
			\end{framed}
		\end{response}

		\begin{point}
			In Remark~\ref{M-re:subband_tradeoff}, the meaning of the sentence, ``there exists a tradeoff for auxiliary link control in the frequency domain'', is not clear to me.
		\end{point}

		\begin{response}
			By `auxiliary link control in the frequency domain', we intended to emphasize that the auxiliary link cannot be designed independently at different frequencies, and a resource allocation opportunity at the channel arises thanks to the IRS. The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). We have added Fig.~\ref{fi:channel_amplitude} and updated the Remark~\ref{M-re:subband_tradeoff} to clarify this point.
			\begin{framed}
				The cascaded channel varies at different frequencies. Since the reflection cannot be designed independently at different subbands, there exists a tradeoff for the passive beamforming design in the frequency domain. The composite channel can be tuned flexibly to meet the specific requirement of multi-carrier SWIPT. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). This is essentially a resource allocation opportunity at the channel enabled by the IRS. In the MISO case, a similar effect also exists in the spatial domain. Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
			\end{framed}
			\label{re:2.10}
		\end{response}

@@

		\begin{response}
			We apologize for the inconvenience. The figures have been amplified and the legends have been calibrated.
		\end{response}

		\begin{point}
			It is said that the reference path loss is \SI{35}{\dB} at \SI{1}{\meter}, while for the center frequency at \SI{5.18}{\GHz}, even adopting the free space path loss model also will lead a much sever path loss at \SI{1}{\meter}. It is not clear how the authors calculate this.
			\label{pt:3.3}
		\end{point}

		\begin{response}
			We agree with the reviewer that the reference path loss used in the simulation is faulty and we sincerely apologize for this issue. The parameter \SI{35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without careful consideration. In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{40}{\dB} at \SI{1}{\meter}. The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards. This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.

			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference. Please refer to the following specification for details.
			\begin{framed}
				We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency where the channel is modeled by IEEE TGn channel model D \cite{M-Erceg2004}. Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards. All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified in model D. The tap gains are modeled as i.i.d. CSCG variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{M-Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search for the R-E region).
			\end{framed}
		\end{response}

@@

		\begin{point}
			The authors considered the practical reflection coefficient beamforming in the simulation results. It is not clear how the authors obtain the discrete phase shift results. Direct quantization method and some other customized optimization techniques for discrete phase shifts may have significant performance gap, see \cite{Wu2020c}. Also, this work adopts the same uniform quantization as the above work, which thus needs to be clarified in the paper.
		\end{point}

		\begin{response}
			Thank you for the clarification. The discrete phase shift is obtained by quantizing the continuous phase shift obtained by Algorithm~\ref{M-al:bcd} to the uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$. We are aware that quantization can lead to performance loss compared with direct optimization over the feasible phase shift set. In the revised manuscript, we have emphasized this point as follows.
			\begin{framed}
				On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients returned by Algorithm~\ref{M-al:bcd} to reduce the circuit complexity and control overhead\footnotemark.
			\end{framed}
			\footnotetext{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS). The readers are referred to \cite{Wu2020c} for details.}
		\end{response}

@@

		\begin{point}
			There are also some other practical phase shift models and nonlinear energy harvesting models such as saturation model for IRS-aided SWIPT in existing works, which may be discussed as related works such as amplitude-dependent phase shift model.
		\end{point}

		\begin{response}
			We have added reference \cite{Xu2021} in the updated manuscript that models the saturation effect of energy harvesters and physical properties of the IRS. Its contributions have been summarized in the manuscript as follows.
			\begin{framed}
				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity. It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
			\end{framed}
			The future works has been updated as follows.
			\begin{framed}
				Also, harvester saturation effect and more involved IRS model based on direction- and frequency-dependent reflection \cite{M-Abeywickrama2020} and/or partially/fully-connected reflection \cite{M-Shen2020a} could be considered in future works.
			\end{framed}
		\end{response}

@@

		\begin{point}
			Some early magazine papers and recent tutorial papers related to IRS-aided WPT/WIT may be further discussed.
		\end{point}

		\begin{response}
			We have incorporated those references into the manuscript as follows.
			\begin{framed}
				\textellipsis The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}.
